Perceptions of Information Disclosure Risks for Wearable Devices

### 2016-01-29 USEC2016-camera-ready/camera-ready.tex
fix < and > errors

\begin{quotation}
\noindent
\textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}
\end{quotation}

@@

We combined 72 data types (<data>) with 4 data recipients (<recipient>) to form a pool of 288 scenarios (Table \ref{all-vur}). Each participant answered 6 questions that were randomly drawn from this pool, displayed in random order. We clarified for our participants that ``app'' meant the app's server, and that the data was not shared with anyone else.

@@

%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper. We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
\hline
Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
\hline
Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
\hline
\end{tabular}
\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
\label{recipient-chi}
\end{center}
\end{table}

@@

\noindent {\bfseries Demographics Factors}
We see that privacy is a main concern for wearables users. Additionally, we show that privacy preferences should also be a consideration when configuring a user's device. A participant's self-reported level of privacy concern---as determined by the IUIPC scale~\cite{malhotra2004internet}---is the biggest demographic predictor of VURs. A Spearman correlation yielded a statistically significant effect between average IUIPC scores and average VUR ($\rho=0.446$, $p<0.0005$), which suggests responses to questions were mostly based on privacy preferences. Additionally, we observed that age was another significant predictor of VUR ($\rho=0.121$, $p<0.0005$), but we suspect that this effect is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$). Others have observed that older individuals tend to be more privacy protective~\cite{varian2005demographics}.

While we initially observed an effect on VURs based on whether or not participants claimed to already own wearables (57.0\% vs. 60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$). The effect of a participant's gender also did not remain significant upon correcting for multiple testing. We observed no correlation between a participant's education level and VUR.\\

@@

\begin{table}[t]
\centering
\begin{tabular}{|l| r| r| r|}
\hline
Parameters & $\chi^2$ & $df$ & QIC\\
\hline
\hline
(Intercept) & 423.96 & 1 & 13,209.1\\
\hline
(Intercept) & 207.07 & 1 & 12,551.49\\
IUIPC (covariate) & 368.5 & 1 & \\
Gender (covariate) & 6.30 & 1 & \\
\hline
(Intercept) & 411.66 & 1 &12,458.86\\
Data Recipient & 599.72 & 3 & \\
\hline
(Intercept) & 418.02 & 1 & 11,382.75\\
Data Type & 1,141.40 & 71 & \\
\hline
(Intercept) & 66.18 & 1 & 9,609.65 \\
Data Recipient & 617.25 & 3 & \\
Data Type & 1,288.51 & 71 & \\
IUIPC (covariate) & 105.73 & 1 & \\
Gender (covariate) & 9.74 & 1 & \\
IUIPC $\times$ Gender & 8.33 & 1 &\\
\hline
\end{tabular}
\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures. The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model. Each parameter listed was statistically significant at $p<0.005$.}
\label{regression}
\end{table}

@@

\begin{table}[t]
\centering
\begin{tabular}{|l| r| r| r|}
\hline
Parameters & $\chi^2$ & $df$ & QIC\\
\hline
\hline
(Intercept) & 442.66 & 1 & 12,727.42\\
Risk & 405.18 & 4 & \\
\hline
(Intercept) & 380.39 & 1 & 12,681.86\\
Data Category & 439.45 & 5 & \\
\hline
(Intercept) & 256.15 & 1 & 12,061.87\\
Risk & 157.84 & 4 & \\
Data Category & 183.90 & 5 & \\
Risk $\times$ Data Category & 259.81 & 8 & \\
\hline
(Intercept) & 62.65 & 1 & 10,406.35\\
Risk & 205.21 & 4 & \\
Data Category & 250.35 & 5 & \\
Recipient & 546.89 & 3 & \\
IUIPC (covariate) & 103.94 & 1 & \\
Gender (covariate) & 9.80 & 1 & \\
IUIPC $\times$ Gender & 8.21 & 1 & \\
Risk $\times$ Data Category & 303.44 & 8 & \\
Recipient $\times$ Risk & 39.14 & 12 & \\
\hline
\end{tabular}
\caption{Metrics for additional binary logistic models of our data using general estimating equations to account for repeated measures. The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model. Each parameter listed was statistically significant at $p<0.005$.}
\label{regression2}
\end{table}

>>>>

\begin{quotation}
\noindent
\textit{``How would you feel if an app on your Cubetastic3000 learned (data) and shared it with (recipient), without asking you first?''}
\end{quotation}

@@

We combined 72 data types, ({\it data}), with 4 data recipients, ({\it recipient}), to form a pool of 288 scenarios (Table \ref{all-vur}). Each participant answered 6 questions that were randomly drawn from this pool, displayed in random order. We clarified for our participants that ``app'' meant the app's server, and that the data was not shared with anyone else.

@@

%A statistical analysis regarding the significance and confidence of data types with respect to all 72 was not performed due to the space constraints of the paper. We do consider all data categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
\hline
Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
\hline
Work-App	& 565.910 & \textless0.0001 & 5,083 & 0.111\\
Public-App	& 481.776 & \textless0.0001 & 5,1988& 0.093\\
Friends-App & 381.653 & \textless0.0001 & 5,096 & 0.075\\
Friends-Work & 20.39 & \textless0.0001 & 5,037 & 0.004\\
Friends-Public & 5.41 & \textless0.0200 & 5,142 & 0.001\\
Work-Public&  5.00 & \textless0.0253 & 5,129	& 0.001\\
\hline
\end{tabular}
\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
\label{recipient-chi}
\end{center}
\end{table}

@@

\noindent {\bfseries Demographics Factors}
We see that privacy is a main concern for wearables users. Additionally, we show that privacy preferences should also be a consideration when configuring a user's device. A participant's self-reported level of privacy concern---as determined by the IUIPC scale~\cite{malhotra2004internet}---is the biggest demographic predictor of VURs. A Spearman correlation yielded a statistically significant effect between average IUIPC scores and average VUR ($\rho=0.446$, $p\textless0.0005$), which suggests responses to questions were mostly based on privacy preferences. Additionally, we observed that age was another significant predictor of VUR ($\rho=0.121$, $p\textless0.0005$), but we suspect that this effect is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p\textless0.0005$). Others have observed that older individuals tend to be more privacy protective~\cite{varian2005demographics}.

While we initially observed an effect on VURs based on whether or not participants claimed to already own wearables (57.0\% vs. 60.8\%, respectively; Mann-Whitney $U=202,896$, $p\textless0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$). The effect of a participant's gender also did not remain significant upon correcting for multiple testing. We observed no correlation between a participant's education level and VUR.\\

@@

\begin{table}[t]
\centering
\begin{tabular}{|l| r| r| r|}
\hline
Parameters & $\chi^2$ & $df$ & QIC\\
\hline
\hline
(Intercept) & 423.96 & 1 & 13,209.1\\
\hline
(Intercept) & 207.07 & 1 & 12,551.49\\
IUIPC (covariate) & 368.5 & 1 & \\
Gender (covariate) & 6.30 & 1 & \\
\hline
(Intercept) & 411.66 & 1 &12,458.86\\
Data Recipient & 599.72 & 3 & \\
\hline
(Intercept) & 418.02 & 1 & 11,382.75\\
Data Type & 1,141.40 & 71 & \\
\hline
(Intercept) & 66.18 & 1 & 9,609.65 \\
Data Recipient & 617.25 & 3 & \\
Data Type & 1,288.51 & 71 & \\
IUIPC (covariate) & 105.73 & 1 & \\
Gender (covariate) & 9.74 & 1 & \\
IUIPC $\times$ Gender & 8.33 & 1 &\\
\hline
\end{tabular}
\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures. The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model. Each parameter listed was statistically significant at $p\textless0.005$.}
\label{regression}
\end{table}

@@

\begin{table}[t]
\centering
\begin{tabular}{|l| r| r| r|}
\hline
Parameters & $\chi^2$ & $df$ & QIC\\
\hline
\hline
(Intercept) & 442.66 & 1 & 12,727.42\\
Risk & 405.18 & 4 & \\
\hline
(Intercept) & 380.39 & 1 & 12,681.86\\
Data Category & 439.45 & 5 & \\
\hline
(Intercept) & 256.15 & 1 & 12,061.87\\
Risk & 157.84 & 4 & \\
Data Category & 183.90 & 5 & \\
Risk $\times$ Data Category & 259.81 & 8 & \\
\hline
(Intercept) & 62.65 & 1 & 10,406.35\\
Risk & 205.21 & 4 & \\
Data Category & 250.35 & 5 & \\
Recipient & 546.89 & 3 & \\
IUIPC (covariate) & 103.94 & 1 & \\
Gender (covariate) & 9.80 & 1 & \\
IUIPC $\times$ Gender & 8.21 & 1 & \\
Risk $\times$ Data Category & 303.44 & 8 & \\
Recipient $\times$ Risk & 39.14 & 12 & \\
\hline
\end{tabular}
\caption{Metrics for additional binary logistic models of our data using general estimating equations to account for repeated measures. The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model. Each parameter listed was statistically significant at $p\textless0.005$.}
\label{regression2}
\end{table}
